---
title: "polygrams"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(out.width='750px', dpi=200)
```
The polygrams package includes function for handling of *Bernstein polygrams*, a class of non-parametric density estimators. 

## Installation
From inside `R`, the package can be installed from GitHub by using devtools.

```{r installation, eval=FALSE}
library("devtools")
install_github("JonasMoss/polygrams")
```


## Usage
The core function is `polygram`, which calculates a polygram based on the supplied `data`, which is its first argument. When `data` has supported different form [0,1], you should consider supplying it with the argument `support`. `s` specifies the positions of the split points, or number of split points if an integer. `m` specifies the degree of the Bernstein polynomials, and defaults to 3, while `p` specifies the degree of connectedness between adjacent bins.

For selecting `s`, the function `elbow_plot`  is supplied. Generics such as `plot` should work well enough, and functions such as `dpolygram`, `ppolygram`  and `rpolygram`  work as well. The exception is `qpolygram` which hasn't been implemented yet.

For functionality such as shape constraints, check the documentation of `polygram`. For more information, type `??polygrams` in the `R` console.

## Example usage

Load the library as is usually done.

```{r polygrams}
library("polygrams")
```

As an application, we study the monthly sunspot data.

```{r data}
dat = datasets::sunspot.month
summary(dat)
```

Based on the summary we choose the support [0,270]. Let's try |s| = 10:

```{r plot}
plot(polygram(dat, support = c(0, 270), s = 10))
```

This density could be convex and monotone:

```{r plot_monotone}
plot(polygram(dat, support = c(0, 270), s = 10, shape = "convex", monotone = "decreasing"))
```
